Flabby and injective objects in toposes

### 2019-03-03 paper-flabby-objects.tex
Be more economical in the use of packages
typo

\usepackage[utf8]{inputenc}
\usepackage{amsthm,mathtools,tikz,float,caption,stmaryrd}
\usetikzlibrary{patterns,matrix,decorations.pathreplacing}
\usepackage[all]{xy}
\usepackage[protrusion=true,expansion=true]{microtype}
\usepackage{hyperref}
\usepackage{xspace}

@@

However, it is an open question under which circumstances quotient inductive
types can be shown to exist. Zermelo--Fraenkel with choice certainly suffices,
while Zermelo--Fraenkel without choice does not~\cite[Section~9]{shulman-lumsdaine:hits},
hence IZF also does not.\footnote{With quotient inductive types, any infinitary
algebraic theory admits free algebras. However, it is consistent with
Zermelo--Fraenkel set theory that some such theories do not admit free
algebras~\cite{blass:free-algebras}.} The existence of quotient inductive types
seem to be, as the existence of enough injective modules, \emph{constructively
neutral}.

>>>>

\usepackage[utf8]{inputenc}
\usepackage{amsthm,mathtools,stmaryrd}
\usepackage[all]{xy}
\usepackage[protrusion=true,expansion=true]{microtype}
\usepackage{hyperref}
\usepackage{xspace}

@@

However, it is an open question under which circumstances quotient inductive
types can be shown to exist. Zermelo--Fraenkel with choice certainly suffices,
while Zermelo--Fraenkel without choice does not~\cite[Section~9]{shulman-lumsdaine:hits},
hence IZF also does not.\footnote{With quotient inductive types, any infinitary
algebraic theory admits free algebras. However, it is consistent with
Zermelo--Fraenkel set theory that some such theories do not admit free
algebras~\cite{blass:free-algebras}.} The existence of quotient inductive types
seems to be, as the existence of enough injective modules, \emph{constructively
neutral}.
